\Title

### 2020-03-05 manuscript/manuscript.tex
Replace hlines and clines for rules
Replace first hline of the table for a toprule, the clines for cmidrules
and hlines on the body of the table for midrules.

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c l l c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \textbf{Parameters}
            & \textbf{Values}
            & \textbf{Increment} \\
        \hline

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \GroundSourceBellowDataConstantDepthDepth
                & \GroundSourceBellowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataConstantDepthDamping
                & \GroundSourceBellowDataConstantDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \GroundSourceBellowDataRelativeDepthDepth
                & \GroundSourceBellowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataRelativeDepthDamping
                & \GroundSourceBellowDataRelativeDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \GroundSourceBellowDataVariableDepthDepth
                & \GroundSourceBellowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \GroundSourceBellowDataVariableDepthDepthFactor
                & \GroundSourceBellowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \GroundSourceBellowDataVariableDepthKNearest
                & \GroundSourceBellowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataVariableDepthDamping
                & \GroundSourceBellowDataVariableDepthDampingIncrement \\
        \hline

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesConstantDepthDepth
                & \GroundBlockMedianSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesConstantDepthSpacing
                & \GroundBlockMedianSourcesConstantDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesConstantDepthDamping
                & \GroundBlockMedianSourcesConstantDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesRelativeDepthDepth
                & \GroundBlockMedianSourcesRelativeDepthDepthIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \GroundBlockMedianSourcesRelativeDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesRelativeDepthDamping
                & \GroundBlockMedianSourcesRelativeDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesVariableDepthDepth
                & \GroundBlockMedianSourcesVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \GroundBlockMedianSourcesVariableDepthDepthFactor
                & \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \GroundBlockMedianSourcesVariableDepthKNearest
                & \GroundBlockMedianSourcesVariableDepthKNearestIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesVariableDepthSpacing
                & \GroundBlockMedianSourcesVariableDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesVariableDepthDamping
                & \GroundBlockMedianSourcesVariableDepthDampingIncrement \\
        \hline

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c l l c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \textbf{Parameters}
            & \textbf{Values}
            & \textbf{Increment} \\
        \hline

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \AirborneSourceBellowDataConstantDepthDepth
                & \AirborneSourceBellowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataConstantDepthDamping
                & \AirborneSourceBellowDataConstantDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \AirborneSourceBellowDataRelativeDepthDepth
                & \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataRelativeDepthDamping
                & \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \AirborneSourceBellowDataVariableDepthDepth
                & \AirborneSourceBellowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneSourceBellowDataVariableDepthDepthFactor
                & \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneSourceBellowDataVariableDepthKNearest
                & \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataVariableDepthDamping
                & \AirborneSourceBellowDataVariableDepthDampingIncrement \\
        \hline

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesConstantDepthDepth
                & \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesConstantDepthSpacing
                & \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesConstantDepthDamping
                & \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesRelativeDepthDepth
                & \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesRelativeDepthSpacing
                & \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesRelativeDepthDamping
                & \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
            \cline{2-5}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesVariableDepthDepth
                & \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneBlockMedianSourcesVariableDepthKNearest
                & \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesVariableDepthSpacing
                & \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesVariableDepthDamping
                & \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
        \hline

>>>>

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c l l c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \textbf{Parameters}
            & \textbf{Values}
            & \textbf{Increment} \\
        \toprule

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \GroundSourceBellowDataConstantDepthDepth
                & \GroundSourceBellowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataConstantDepthDamping
                & \GroundSourceBellowDataConstantDepthDampingIncrement \\
            \cmidrule{2-5}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \GroundSourceBellowDataRelativeDepthDepth
                & \GroundSourceBellowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataRelativeDepthDamping
                & \GroundSourceBellowDataRelativeDepthDampingIncrement \\
            \cmidrule{2-5}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \GroundSourceBellowDataVariableDepthDepth
                & \GroundSourceBellowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \GroundSourceBellowDataVariableDepthDepthFactor
                & \GroundSourceBellowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \GroundSourceBellowDataVariableDepthKNearest
                & \GroundSourceBellowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \GroundSourceBellowDataVariableDepthDamping
                & \GroundSourceBellowDataVariableDepthDampingIncrement \\
        \midrule

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesConstantDepthDepth
                & \GroundBlockMedianSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesConstantDepthSpacing
                & \GroundBlockMedianSourcesConstantDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesConstantDepthDamping
                & \GroundBlockMedianSourcesConstantDepthDampingIncrement \\
            \cmidrule{2-5}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesRelativeDepthDepth
                & \GroundBlockMedianSourcesRelativeDepthDepthIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \GroundBlockMedianSourcesRelativeDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesRelativeDepthDamping
                & \GroundBlockMedianSourcesRelativeDepthDampingIncrement \\
            \cmidrule{2-5}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \GroundBlockMedianSourcesVariableDepthDepth
                & \GroundBlockMedianSourcesVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \GroundBlockMedianSourcesVariableDepthDepthFactor
                & \GroundBlockMedianSourcesVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \GroundBlockMedianSourcesVariableDepthKNearest
                & \GroundBlockMedianSourcesVariableDepthKNearestIncrement \\
            &
                & Spacing (m)
                & \GroundBlockMedianSourcesVariableDepthSpacing
                & \GroundBlockMedianSourcesVariableDepthSpacingIncrement \\
            &
                & Damping
                & \GroundBlockMedianSourcesVariableDepthDamping
                & \GroundBlockMedianSourcesVariableDepthDampingIncrement \\
        \midrule

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c l l c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \textbf{Parameters}
            & \textbf{Values}
            & \textbf{Increment} \\
        \toprule

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \AirborneSourceBellowDataConstantDepthDepth
                & \AirborneSourceBellowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataConstantDepthDamping
                & \AirborneSourceBellowDataConstantDepthDampingIncrement \\
            \cmidrule{2-5}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \AirborneSourceBellowDataRelativeDepthDepth
                & \AirborneSourceBellowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataRelativeDepthDamping
                & \AirborneSourceBellowDataRelativeDepthDampingIncrement \\
            \cmidrule{2-5}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \AirborneSourceBellowDataVariableDepthDepth
                & \AirborneSourceBellowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneSourceBellowDataVariableDepthDepthFactor
                & \AirborneSourceBellowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneSourceBellowDataVariableDepthKNearest
                & \AirborneSourceBellowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \AirborneSourceBellowDataVariableDepthDamping
                & \AirborneSourceBellowDataVariableDepthDampingIncrement \\
        \midrule

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesConstantDepthDepth
                & \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesConstantDepthSpacing
                & \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesConstantDepthDamping
                & \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
            \cmidrule{2-5}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesRelativeDepthDepth
                & \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesRelativeDepthSpacing
                & \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesRelativeDepthDamping
                & \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
            \cmidrule{2-5}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesVariableDepthDepth
                & \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneBlockMedianSourcesVariableDepthKNearest
                & \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesVariableDepthSpacing
                & \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesVariableDepthDamping
                & \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
        \midrule
